Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise

### 2016-09-06 main.tex
WIP discussion

\rightheader{Gaing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}

@@

Remarkably (and in line with the literature reviewed in
section~\ref{cognitive-priming}), these cognitive ascriptions lead to a visible
change in the participants' behaviour: they gaze more at the head of the robot
when they watch a scene that elicits stronger anthropomorphic attributions.
Several explanations can be thought of. At an abstract level, the head may
typically be seen as embodying the mind and the emotions. As such, the head of
an agent that is believed to be endowed with such cognitive and emotional
abilities could be thought to be of higher importance, attracting more
attention. Another explanation pertains to the social norms elicited by a moral
agent~\citep{malle2014moral}. We can reasonably suppose that a robot thought to
be endowed with rich cognitive skills is likely to be considered more as a moral
agent as a robot with an apparent mechanical behaviour. As a result, the
participant might be led to adhere to social norms (including looking at the
face when interacting) when watching the robot. A third explanation involves
automatic social behaviours: if the participant is tricked into believing that
the robot might have rich cognitive skills, she might automatically search for
even more socio-cognitive cues, and the face is a particularly rich source of
such cues (facial expressions, gaze, back-channel communication like nodding).

>>>>

\rightheader{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}

@@

Remarkably (and in line with the literature reviewed in
section~\ref{cognitive-priming}), these cognitive ascriptions lead to a visible
change in the participants' behaviour: they gaze more at the head of the robot
when they watch a scene that elicits stronger anthropomorphic attributions.
Several explanations can be thought of. At an abstract level, the head may
typically be seen as embodying the mind and the emotions. As such, the head of
an agent that is believed to be endowed with such cognitive and emotional
abilities could be thought to be of higher importance, attracting more
attention. Another explanation pertains to the social norms elicited by a moral
agent~\citep{malle2014moral}. We can reasonably suppose that a robot thought to
be endowed with rich cognitive skills is likely to be considered more as a moral
agent as a robot with an apparent mechanical behaviour. As a result, the
participant might be led to adhere to social norms (including looking at the
face when interacting) when watching the robot. A third explanation involves
automatic social behaviours: if the participant is tricked into believing that
the robot might have a richer set of cognitive skills, she might automatically
search for other socio-cognitive confirmation cues, and the face is a
particularly rich source of such cues (facial expressions, gaze, back-channel
communication like nodding). This would therefore also lead to longer observed
gaze fixations on the robot's head.

Our experimental protocol enabled us to examine two additional questions: by
administrating the Godspeed questionnaire on anthropomorphism and mind
attribution first as pre-test, we gained a picture of the initial tendency of
our participants to anthropomorphise robots. Using our \deltaant measure of the
gazing behaviour similarity, we have evidenced that people with an higher
tendency to anthropomorphise robots, also exhibit a more similar gazing
behaviour when they watch either a human or a robot performing the same task. If
confirmed (in particular with balanced human genders), this is a significant
result. The Godspeed questionnaire assesses how likely we are to
anthropomorphise machines in an abstract way: no concrete robots nor interaction
situations are shown; the participants might react to the sentence ``Please rate
your impression of robots'' in widely different ways depending on their own
constructed images of what robots are. And yet, our results show a significant
correlation with gazing behaviour: the more you tend to anthropomorphise, the
more you look at robots the way you look at humans. This implies that the mere
propensity to attribute physical or mental human traits to robots suffice to
influence a mostly unconscious (yet easy to observe) physical behaviour.  This
link between psychological attributions and a resulting physical behaviour might
be of interest to the Human-Robot Interaction community, especially if we endow
the robot with the ability to measure itself, \emph{during} the interaction, the
time spent by the human on its face. This would for instance allow the robot to
build an initial model of the cognitive expectations held by the human regarding
the robot.
